%---styling---
\documentclass{article}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{multicol}
\usepackage[margin=0.2in]{geometry}
\usepackage{fontawesome}
\usepackage[none]{hyphenat}
\usepackage{nopageno}
\usepackage{hyperref}
\usepackage{paralist}
\hypersetup{
	pdftoolbar=false,
	pdfmenubar=false,
	pdftitle={Jake Hempel},
	pdfauthor={Jake Hempel},
	pdfsubject={Resume},
	colorlinks=false,
	pdfnewwindow=true,
	pdfkeywords={Information Technology} {System Administration} {Cyber Security} {Cyber} {Networking}
}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{}
{}
{0em}
{\underline}

\titleformat{\subsubsection}[runin]
{}
{}
{0em}
{}

%---begin resume---
\begin{document}
\begin{samepage}
\begin{center}
%\Huge{\textbf{R\'esum\'e}} \\*
\huge{\textbf{Jake Hempel}} \\*
\large{\faEnvelope \, \href{mailto:mail@jakehempel.com}{mail@jakehempel.com}
\faGlobe \, \href{https://jakehempel.com}{jakehempel.com}}
\faLinkedinSquare \, \href{https://www.linkedin.com/in/jake-hempel/}{jake-hempel}
\end{center}

\section{Experience}
\subsection{SPS Technologies (Precision Castparts Corp) -- Systems Administrator/Network Administrator[April 2021 - Current]}
\begin{compactitem}
	\item Oversee all IT operations and projects for two 24/7 facilities, supporting 500+ endpoints and 40+ servers hosting mission critical factory applications in a SOX controlled DoD contracting facility.
	\item Member of division LAN team; conducting routine network engineering tasks via Juniper MIST and CLI, managing wireless infrastructure via Extreme Networks, troubleshooting network errors, and creating network documentation.
	\item Participates in corporation wide networking projects; including segmentation, infrastructure upgrades, and site build-outs.
	\item Utilize SIEM and monitoring software such as Splunk, Solarwinds, and Lansweeper to identify and remediate security vulnerabilities.
\end{compactitem}
\subsection{PTS Data Center Solutions -- Jr. System Administrator [August 2019 - April 2021]}
\begin{compactitem}
	\item Oversaw the IT operations of 4 SMB's, with mixed Windows, Linux, and VMWare vSphere environments.
	\item Primary security engineer, worked under guidance of information security partner to remediate vulnerabilities and conduct incident response as primary company contact.
	\item Ensured compliance with backup SLA's for all customers via Veaam Backup and Replication.
	\item Provided tier 3 help desk support for customers troubleshooting server and desktop issues.
\end{compactitem}
\subsection{Passaic County Prosecutor's Office -- Homeland Security and Intelligence Unit [May 2018 - August 2018]}
\begin{compactitem}
	\item Conducted open source intelligence gathering on behalf of the unit.
	\item Developed and implemented internal case docket management system utilizing Drupal CMS.
	\item Assisted Urban Area Security Initiative with developing a training platform utilizing Moodle LMS.
\end{compactitem}
\subsection{Rutgers Digital Classroom Services -- Build Team/Support Specialist [April 2017 - May 2019]}
\begin{compactitem}
	\item Following wiring diagrams, ensured all components were properly connected and tested, as well as spliced custom cables.
	\item Assisted with two summer wide infrastructure overhauls for all 5 of Rutgers New Brunswick's campuses, being involved with over 80 podium demolitions and reconstructions.
	\item Provided campus-wide end-user technical support and training for DCS podiums in 5 lecture halls.
\end{compactitem}

\section{Education}
\noindent%
\begin{minipage}[t]{.55\textwidth}
	\subsection*{University}
	\textbf{Rutgers University - New Brunswick, NJ} \\
	\textbf{Major} Information Technology and Informatics \\
	\textbf{Minor} Critical Intelligence Studies minor \\
	September 2015 -- May 2019
\end{minipage}%
\hfill
\begin{minipage}[t]{.35\textwidth}
	\subsection*{Certifications}
	Juniper Networks JNCIA-Junos \\
	Juniper Networks JNCIA-MistAI \\
	FCC Amateur Radio Technician
\end{minipage}%

\section{Skills}

\subsection{Infrastructure}
\begin{description}
\item[Operating Systems] Windows, Windows Server (2008, 2012, 2016, 2019), Linux (Debian, Ubuntu, Kali, Raspian, CentOS), Unix,  macOS, Android
\item[Server Software] Apache2, Nginx, Samba, Active Directory, Microsoft Exchange, Dell Wyse Management Suite
\item[Virtualization] vSphere Suite (ESXI 6.0-7.0, vCenter, vCloud Director), VMware Horizon, VirtualBox, Docker
\item[Networking] Juniper(Junos OS, MIST, EX Series switches, SRX Firewalls), Extreme Networks, Aruba Networks, pfSense, OpenWrt
\end{description}

\subsection{Software}

\begin{description}
\item[Applications] Microsoft Office Suite, Git, PuTTY/SSH, Wireshark, Microsoft Deployment Toolkit, Veeam Backup and Replication, Splunk, Lansweeper, SolarWinds, Nessus, Ansible
\item[Content Management Systems] WordPress, Drupal, Moodle, Jekyll
\item[Scripting and Programming] Python, Bash, PowerShell, Java, C++, HTML, CSS, Markdown, XML, {\LaTeX}
\end{description}


\begin{center}
\textbf{References available upon request.}
\end{center}

\thispagestyle{empty}
\end{samepage}
\end{document}
%\grid
